Estimating real-time highstreet footfall from Wi-Fi probe requests

### 2018-06-26 paper/sections/main_study.tex
signal strength complete

\subsection{signal strength filtering}
First we see the distribution of the signal strength varies with location and configuration. 
The density plot for signal strength is shown alogn with configuration in figure.
We can see that the signal strength distribution shows distinct patterns of high and low when the installation is that there is a clear distant source of noise but this distinction get more and more obscure as we move towards difficult installations. 
For example, location 2 is almost a normally distributed noise as it is too far to pick up any pedestrians but location 5 with a clear view of footpath and a phone shop next door shows clear distinction between the two. 
Intuitively the classfication algorithm should give us better results in the latter. 
It is important to note that we are dealing with relative singal strengths, this can vary with location and time of the analysis but we should be still be able to differentiate signal from noise. 
We run the kmeans classification algorithm and filter out the probe requests which are randomised and have signal strengths less than the second break (or the threshold). 
We then count the number of Unique MAC addresses present in every minute and remove MAC addreses which reappear within 30 minutes of previous appearance. 
We then compare this with the minute by minute aggreagation for the manual counts and find the average error per minute for the sensor count. 
The results are shown in the table.We see that the location XXXX has the most error while location XXX has the least error confirming our intuition. 
We also see that the error follows the complexity of the installation. 
It is also very promising that this method alone reduces our margin of error by a lot. 
For some practical purposes which does not require absolute numbers, this should be sufficient. talk about examples of indexes and dashboards and short term trends.

@@

>>>>

\subsection{signal strength filtering}
First we see how the distribution of the signal strength varies with location and configuration. 
The density plot for signal strength is shown alogn with configuration in figure.
We can see that the signal strength distribution shows distinct patterns of high and low when the installation is that there is a clear distant source of noise but this distinction get more and more obscure as we move towards difficult installations. 
For example, location 2 is almost a normally distributed noise as it is too far to pick up any pedestrians but location 5 with a clear view of footpath and a phone shop next door shows clear distinction between the two. 
Intuitively the classfication algorithm should give us better results in the latter. 
It is important to note that we are dealing with relative singal strengths, this can vary with location and time of the analysis but we should be still be able to differentiate signal from noise. 
We run the kmeans classification algorithm and filter out the probe requests which are randomised and have signal strengths less than the second break (or the threshold). 
We then count the number of Unique MAC addresses present in every minute and remove MAC addreses which reappear within 30 minutes of previous appearance. 
We then compare this with the minute by minute aggreagation for the manual counts and find the average error per minute for the sensor count. 
The results are shown in the table.We see that the location XXXX has the most error while location XXX has the least error confirming our intuition. 
We also see that the error follows the complexity of the installation. 
It is also very promising that this method alone reduces our margin of error by a lot. 
For some practical purposes which does not require absolute numbers, this should be sufficient. talk about examples of indexes and dashboards and short term trends.

@@

\begin{table}
	\tbl{Data collected at different locations and the correspondin mean absolute percentage error after each filtering process}
	{\begin{tabular}{cccc} 
		\toprule
			Sensor& MAPE - No Cleaning (\%)&MAPE - Signal Strength (\%)&MAPE - Clustering (\%)\\
		 \midrule
			1 & 211 &  56 & \\
			2 & 934 & 400 & \\
			3 &  88 &  -3 & \\
			4 & 501 & 237 & \\
			5 & 476 & 117 & \\
		 \bottomrule
	\end{tabular}}
	\label{errors-table}
\end{table}
